Information Disclosure in Dynamic Innovation Contests

### 2025-05-26 paper/Paper.tex
update-paper

\begin{table}[htbp]
\newcolumntype{Y}{>{\centering\arraybackslash}X}
\centering
\caption{Bayesian Estimates from Synthetic Data}\label{tbl-contest90}
\begin{tabularx}{\textwidth}{lYYYYYY}
\toprule
\textbf{Parameters} & \textbf{$c_i$} & \textbf{$c_j$} & \textbf{$r$} & \textbf{$\sigma$} & \textbf{$\lambda$} & \textbf{$\mu_0$} \\
\addlinespace[0.25ex]
\cline{2-7}
\addlinespace[0.25ex]
(true val.)        & 1.2 & 1.5 & 15.0 & 2.0 & 1.0 & 0.0 \\
\midrule
 Posterior Mean    & 1.078 & 1.711 & 14.645 & 2.777 & 1.103 & -0.010 \\
 Posterior Std.       & 0.382 & 0.661 & 3.986 & 0.503 & 0.303 & 2.026 \\
 RMSE                  & 0.401 & 0.694 & 4.002 & 0.925 & 0.320 & 2.026 \\
 95\% Interval        
		& [0.55, 1.99] 
		& [0.77, 3.30]
		& [7.8, 23.0]
		& [1.94, 3.93]
		& [0.61, 1.79] 
		& [-3.97, 4.00] \\
\bottomrule
\addlinespace[0.5ex]
\end{tabularx}
\begin{minipage}{\textwidth}
{\footnotesize
\textit{Note:} $\text{MSE}(\hat\theta) = \mathbb{E}(\hat{\theta}-\theta)^2 = [\mathbb{E}(\hat{\theta}) - \theta]^2 + Var(\hat{\theta})$ by the bias–variance decomposition. RMSE is then calculate by the squared root of MSE. 
}
\end{minipage}
\end{table}

@@

\begin{table}[htbp]
\newcolumntype{Y}{>{\centering\arraybackslash}X}
\centering
\caption{Bayesian Estimates from Pooled Synthetic Data}\label{tbl-pool-synthetic-data}
\begin{tabularx}{\textwidth}{lYYYYYY}
\toprule
\textbf{Parameters} & \textbf{$c_i$} & \textbf{$c_j$} & \textbf{$r$} & \textbf{$\sigma$} & \textbf{$\lambda$} & \textbf{$\mu_0$}\\
\addlinespace[0.25ex]
\cline{2-7}
\addlinespace[0.25ex]
(true val.)        & 1.2 & 1.5 & 15.0 & 2.0 & 1.0 & 0.0\\
\midrule
\addlinespace
\multicolumn{5}{l}{\textbf{Pool of 5 Contests}} \\
Posterior Mean  & 1.215 & 1.647 && 1.969 & 1.079 &\\
Posterior Std.    & 0.120 & 0.178 && 0.143 & 0.130 &\\
RMSE               & 0.121 & 0.231 && 0.146 & 0.152 &\\
\addlinespace
\multicolumn{5}{l}{\textbf{Pool of 10 Contests}} \\
Posterior Mean  & 1.255 & 1.690 && 1.911 & 1.053 &\\
Posterior Std.    & 0.090 & 0.129 && 0.096 & 0.090 &\\
RMSE               & 0.105 & 0.230 && 0.131 & 0.105 &\\
\addlinespace
\multicolumn{5}{l}{\textbf{Pool of 20 Contests}} \\
Posterior Mean  & 1.206 & 1.639 && 1.981 & 0.990 &\\
Posterior Std.    & 0.059 & 0.090 && 0.069 & 0.059 &\\
RMSE               & 0.060 & 0.165 && 0.071 & 0.060 &\\
\bottomrule
\addlinespace[0.5ex]
\end{tabularx}
\begin{minipage}{\textwidth}
{\footnotesize
\textit{Note:} $\text{MSE}(\hat\theta) = \mathbb{E}(\hat{\theta}-\theta)^2 = [\mathbb{E}(\hat{\theta}) - \theta]^2 + Var(\hat{\theta})$ by the bias–variance decomposition. RMSE is then calculate by the squared root of MSE. 
}
\end{minipage}
\end{table}

@@

\begin{table}[htbp]
\newcolumntype{Y}{>{\centering\arraybackslash}X}
\centering
\caption{Bayesian Estimates from Long Term Synthetic Data}\label{tbl-longterm-synthetic-data}
\begin{tabularx}{\textwidth}{lYYYYYY}
\toprule
\textbf{Parameters} & \textbf{$c_i$} & \textbf{$c_j$} & \textbf{$r$} & \textbf{$\sigma$} & \textbf{$\lambda$} & \textbf{$\mu_0$}\\
\midrule
\multicolumn{5}{l}{\textbf{Contest of 6 Months}} \\
True Value           & 0.6     & 0.75   & 15.0 & 2.0     & 1.0     & 0.0\\
Posterior Mean    & 0.840 & 0.835 & . & 1.944 & 1.142 &\\
Posterior Std.       & 0.138 & 0.152 & . & 0.226 & 0.245 &\\
RMSE                  & 0.276 & 0.174 & . & 0.233 & 0.283 &\\
\addlinespace
\multicolumn{5}{l}{\textbf{Contest of 12 Months}} \\
True Value           & 0.3     & 0.375 & . & 2.0     & 1.0     & 0.0\\
Posterior Mean    & 0.307 & 0.341 & . & 2.187 & 1.034 &\\
Posterior Std.      & 0.020 & 0.033 & . & 0.127 & 0.098 &\\
RMSE                  & 0.021 & 0.047 & . & 0.226 & 0.102 &\\
\bottomrule
\addlinespace[0.5ex]
\end{tabularx}
\begin{minipage}{\textwidth}
{\footnotesize
\textit{Note:} (1) $\text{MSE}(\hat\theta) = \mathbb{E}(\hat{\theta}-\theta)^2 = [\mathbb{E}(\hat{\theta}) - \theta]^2 + Var(\hat{\theta})$ by the bias–variance decomposition. RMSE is then calculate by the squared root of MSE. 
(2) Players $i$ and $j$ submit 31 and 40 times in the 6-month contest, and 143 and 182 times in the 12-month contest, respectively.
}
\end{minipage}
\end{table}

@@

By the data generating process (\ref{eq-leaderboard-gap}), we have a simple maximum likelihood estimation (MLE) of the true value of $\lambda$. 
Since $\hat{y}_t - y_t \sim \mathcal{N}(0, 1/(\lambda\Delta))$, we have 
\begin{equation*}
\lambda^{\text{MLE}} = \frac{n}{\Delta\sum^n_{i=1}(y_i - \hat{y}_i)^2}
\end{equation*}

\begin{figure}[!ht]
    \centering
    \begin{subfigure}{0.48\textwidth}
        \centering
        \includegraphics[width=\linewidth]{validate_lamb.pdf}
        \caption{Validate $\lambda$}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.48\textwidth}
        \centering
        \includegraphics[width=\linewidth]{validate_sigma.pdf}
        \caption{Validate $\sigma$}
    \end{subfigure}
    \caption{Structure Validation}
    \label{fig-approximation}
\end{figure}

@@

First, we estimate submission intensities $\tau_i(t)$ and $\tau_j(t)$ by kernel density estimation (KDE). 
Having $\hat{\tau}_i$ and $\hat{\tau}_j$, the effort levels of the two players are simply $m_i(t) = \hat{\tau}_i / r$ and $m_j(t) = \hat{\tau}_j / r$ by (\ref{eq-model-intensity}), where $r$ is the ratio of effort level and submission intensity. 
Next, with the submission times denoted by $\{t_k\}$, we have $y_{t_{k+1}} - y_{t_k} \sim \mathcal{N}\left(\int^{t_{k+1}}_{t_k}m_i(s) - m_j(s)ds, \sigma^2(t_{k+1}-t_k)\right)$ by the dynamic of private leaderboard (\ref{eq-state-dynamics}). 
Then, by (\ref{normal-mle-sigma}), we can estimate the parameters $\sigma$ using MLE: 
\begin{equation*}
\sigma^{\text{MLE}} = \left(\frac{1}{n}\sum_k\frac{\left[y_{t_{k+1}}-y_{t_k}-\int^{t_{k+1}}_{t_k}m_i(s) - m_j(s)ds\right]^2}{t_{k+1}-t_k}\right)^{1/2}
\end{equation*}
where $\hat{r}$ is the Bayesian estimate.

>>>>

\begin{table}[htbp]
\newcolumntype{Y}{>{\centering\arraybackslash}X}
\centering
\caption{Bayesian Estimates from Synthetic Data}\label{tbl-contest90}
\begin{tabularx}{\textwidth}{lYYYYYY}
\toprule
\textbf{Parameters} & \textbf{$c_i$} & \textbf{$c_j$} & \textbf{$r$} & \textbf{$\sigma$} & \textbf{$\lambda$} & \textbf{$\mu_0$} \\
\addlinespace[0.25ex]
\cline{2-7}
\addlinespace[0.25ex]
(true val.)        & 1.2 & 1.5 & 15.0 & 2.0 & 1.0 & 0.0 \\
\midrule
 Posterior Mean    & 1.078 & 1.711 & 14.645 & 2.777 & 1.103 & -0.010 \\
 Posterior Stderr   & 0.382 & 0.661 & 3.986 & 0.503 & 0.303 & 2.026 \\
 RMSE                  & 0.401 & 0.694 & 4.002 & 0.925 & 0.320 & 2.026 \\
 95\% Interval        
		& [0.55, 1.99] 
		& [0.77, 3.30]
		& [7.8, 23.0]
		& [1.94, 3.93]
		& [0.61, 1.79] 
		& [-3.97, 4.00] \\
\bottomrule
\addlinespace[0.5ex]
\end{tabularx}
\begin{minipage}{\textwidth}
{\footnotesize
\textit{Note:} $\text{MSE}(\hat\theta) = \mathbb{E}(\hat{\theta}-\theta)^2 = [\mathbb{E}(\hat{\theta}) - \theta]^2 + Var(\hat{\theta})$ by the bias–variance decomposition. RMSE is then calculate by the squared root of MSE. 
}
\end{minipage}
\end{table}

@@

\begin{table}[htbp]
\newcolumntype{Y}{>{\centering\arraybackslash}X}
\centering
\caption{Bayesian Estimates from Pooled Synthetic Data}\label{tbl-pool-synthetic-data}
\begin{tabularx}{\textwidth}{lYYYYYY}
\toprule
\textbf{Parameters} & \textbf{$c_i$} & \textbf{$c_j$} & \textbf{$r$} & \textbf{$\sigma$} & \textbf{$\lambda$} & \textbf{$\mu_0$}\\
\addlinespace[0.25ex]
\cline{2-7}
\addlinespace[0.25ex]
(true val.)        & 1.2 & 1.5 & 15.0 & 2.0 & 1.0 & 0.0\\
\midrule
\addlinespace
\multicolumn{5}{l}{\textbf{Pool of 5 Contests}} \\
Posterior Mean  & 1.215 & 1.647 && 1.969 & 1.079 &\\
Posterior Stderr & 0.120 & 0.178 && 0.143 & 0.130 &\\
RMSE               & 0.121 & 0.231 && 0.146 & 0.152 &\\
\addlinespace
\multicolumn{5}{l}{\textbf{Pool of 10 Contests}} \\
Posterior Mean  & 1.255 & 1.690 && 1.911 & 1.053 &\\
Posterior Stderr & 0.090 & 0.129 && 0.096 & 0.090 &\\
RMSE                & 0.105 & 0.230 && 0.131 & 0.105 &\\
\addlinespace
\multicolumn{5}{l}{\textbf{Pool of 20 Contests}} \\
Posterior Mean  & 1.206 & 1.639 && 1.981 & 0.990 &\\
Posterior Stderr & 0.059 & 0.090 && 0.069 & 0.059 &\\
RMSE                & 0.060 & 0.165 && 0.071 & 0.060 &\\
\bottomrule
\addlinespace[0.5ex]
\end{tabularx}
\begin{minipage}{\textwidth}
{\footnotesize
\textit{Note:} $\text{MSE}(\hat\theta) = \mathbb{E}(\hat{\theta}-\theta)^2 = [\mathbb{E}(\hat{\theta}) - \theta]^2 + Var(\hat{\theta})$ by the bias–variance decomposition. RMSE is then calculate by the squared root of MSE. 
}
\end{minipage}
\end{table}

@@

\begin{table}[htbp]
\newcolumntype{Y}{>{\centering\arraybackslash}X}
\centering
\caption{Bayesian Estimates from Long Term Synthetic Data}\label{tbl-longterm-synthetic-data}
\begin{tabularx}{\textwidth}{lYYYYYY}
\toprule
\textbf{Parameters} & \textbf{$c_i$} & \textbf{$c_j$} & \textbf{$r$} & \textbf{$\sigma$} & \textbf{$\lambda$} & \textbf{$\mu_0$}\\
\midrule
\multicolumn{5}{l}{\textbf{Contest of 6 Months}} \\
True Value           & 0.6     & 0.75   & 15.0 & 2.0     & 1.0     & 0.0\\
Posterior Mean    & 0.840 & 0.835 & . & 1.944 & 1.142 &\\
Posterior Stderr   & 0.138 & 0.152 & . & 0.226 & 0.245 &\\
RMSE                  & 0.276 & 0.174 & . & 0.233 & 0.283 &\\
\addlinespace
\multicolumn{5}{l}{\textbf{Contest of 12 Months}} \\
True Value           & 0.3     & 0.375 & . & 2.0     & 1.0     & 0.0\\
Posterior Mean    & 0.307 & 0.341 & . & 2.187 & 1.034 &\\
Posterior Stderr   & 0.020 & 0.033 & . & 0.127 & 0.098 &\\
RMSE                  & 0.021 & 0.047 & . & 0.226 & 0.102 &\\
\bottomrule
\addlinespace[0.5ex]
\end{tabularx}
\begin{minipage}{\textwidth}
{\footnotesize
\textit{Note:} (1) $\text{MSE}(\hat\theta) = \mathbb{E}(\hat{\theta}-\theta)^2 = [\mathbb{E}(\hat{\theta}) - \theta]^2 + Var(\hat{\theta})$ by the bias–variance decomposition. RMSE is then calculate by the squared root of MSE. 
(2) Players $i$ and $j$ submit 31 and 40 times in the 6-month contest, and 143 and 182 times in the 12-month contest, respectively.
}
\end{minipage}
\end{table}

@@

By the data generating process (\ref{eq-leaderboard-gap}), we have a simple maximum likelihood estimation (MLE) of the true value of $\lambda$. 
Let $c = {1, 2, ..., n}$ index the contest.
Since $\hat{y}_t^c - y_t^c \sim \mathcal{N}(0, 1/(\lambda_c\Delta))$, we have 
\begin{equation*}
\lambda^{\text{MLE}}_c = \frac{N^c}{\Delta\sum^{N^c}_{k=1}(y_k^c - \hat{y}_k^c)^2}, \quad N^c = T/\Delta
\end{equation*}

Below is the regression result:

%%%%%%%%%% Figure & Table %%%%%%%%%%%
\noindent
\begin{minipage}[t]{0.43\textwidth}
	\vspace*{\fill}
	\centering
	\includegraphics[width=\linewidth]{validate_lamb.pdf}
	\vspace*{\fill}
\end{minipage}
\hfill
\begin{minipage}[t]{0.53\textwidth}
	\vspace*{\fill}
	\centering
	\newcolumntype{Y}{>{\centering\arraybackslash}X}
	\begin{tabularx}{\textwidth}{llYY}
		\toprule
		& coef. & stderr & 95\% CI \\
		\midrule
		const.
		& -0.718 & 3.184 & [-7.064, 5.627] \\
		$\log(1 + \hat{\lambda})$ 
		& 3.259\textbf{**} & 1.089 & [1.089, 5.429] \\
		\midrule
		Obs. & \multicolumn{3}{c}{75} \\
		R$^2$ & \multicolumn{3}{c}{0.109} \\
		Adj. R$^2$ & \multicolumn{3}{c}{0.097} \\
		\bottomrule
		\addlinespace[0.5ex]
	\end{tabularx}
	\begin{minipage}{\textwidth}
{\footnotesize
\textit{Note:} (1) Significance levels: \textbf{***} $p < 0.001$, \textbf{**} $p < 0.01$, \textbf{*} $p < 0.05$. 
(2) Normality diagnostics: Omnibus = 0.376, Jarque-Bera = 0.070, Skewness = $-0.041$, Kurtosis = 3.125. 
(3) Other diagnostic statistics: Condition Number = 28.2, Durbin-Watson = 2.244.
}
	\end{minipage}
	\vspace*{\fill}
\end{minipage}
%%%%%%%%%%%% Captions %%%%%%%%%%%%
\noindent
\begin{minipage}[t]{0.43\textwidth}
	\centering
	\captionof{figure}{...}
\end{minipage}
\hfill
\begin{minipage}[t]{0.53\textwidth}
	\centering
	\captionof{table}{...}
\end{minipage}
\medskip

Result: significantly positively related.

@@

By the dynamic of private leaderboard (\ref{eq-state-dynamics}), with the submission times of contest $c$ denoted by $\{t^c_k\}^{N^c}_{k=1}$, we have $y^c_{k+1} - y^c_{k} \sim \mathcal{N}\left(\int^{t_{k+1}}_{t_k}m^c_i(s) - m^c_j(s)ds, \sigma^2(t^c_{k+1}-t^c_k)\right)$ . 
Then, by (\ref{normal-mle-sigma}), we can estimate the parameters $\sigma$ using MLE: 
\begin{equation*}
\sigma^{\text{MLE}}_c = \left(\frac{1}{N^c}\sum_k\frac{\left[y^c_{t^c_{k+1}}-y^c_{t_k}-\int^{t^c_{k+1}}_{t^c_k}m^c_i(s) - m^c_j(s)ds\right]^2}{t^c_{k+1}-t^c_k}\right)^{1/2}
\end{equation*}
where $\hat{r}$ is the Bayesian estimate.

\noindent
\begin{minipage}[t]{0.43\textwidth}
	\vspace*{\fill}
	\centering
	\includegraphics[width=\linewidth]{validate_sigma.pdf}
	\vspace*{\fill}
\end{minipage}
\hfill
\begin{minipage}[t]{0.53\textwidth}
	\vspace*{\fill}
	\centering
	\newcolumntype{Y}{>{\centering\arraybackslash}X}
	\begin{tabularx}{\textwidth}{llYY}
		\toprule
		& coef. & stderr & 95\% CI \\
		\midrule
		const.
		& 0.054 & 0.116 & [-0.178,0.285] \\
		$\log(1 + \hat{\lambda})$ 
		& 0.887\textbf{***} & 0.152 & [0.583, 1.190] \\
		\midrule
		Obs. & \multicolumn{3}{c}{75} \\
		R$^2$ & \multicolumn{3}{c}{0.317} \\
		Adj. R$^2$ & \multicolumn{3}{c}{0.308} \\
		\bottomrule
		\addlinespace[0.5ex]
	\end{tabularx}
	\begin{minipage}{\textwidth}
{\footnotesize
\textit{Note:} (1) Significance levels: \textbf{***} $p < 0.001$, \textbf{**} $p < 0.01$, \textbf{*} $p < 0.05$. 
(2) Normality diagnostics: Omnibus = 1.280, Jarque-Bera = 0.774, Skewness = 0.225, Kurtosis = 3.214.
(3) Other diagnostic statistics: Condition Number = 5.08, Durbin-Watson = 1.618.
}
	\end{minipage}
	\vspace*{\fill}
\end{minipage}
%%%%%%%%%%%% Captions %%%%%%%%%%%%
\noindent
\begin{minipage}[t]{0.43\textwidth}
	\centering
	\captionof{figure}{...}
\end{minipage}
\hfill
\begin{minipage}[t]{0.53\textwidth}
	\centering
	\captionof{table}{...}
\end{minipage}
\medskip

Result: significantly positively related.
